The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 paper.tex
Change all alpha to alpha_2D in main

for $\alpha^{\parallel}$ and $\alpha^{\perp}$ under small perturbation

@@

  & \alpha^{\parallel} &= \frac{2e^{2}}

@@

  & \alpha^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}

@@

rise to the different relations of $\alpha^{\parallel}$ and
$\alpha^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,

@@

$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the

@@

$\alpha^{\perp}$ is actually proportional to the size of potential

@@

  &\alpha^{\parallel} &\propto E_{g}^{-1} \\

@@

  &\alpha^{\perp} & \propto \delta

@@

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section SXX) \todo{note}, we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.

@@

corresponds well with theoretical investigations
\citenum{Jiang_2017_Eg_Eb} (details see Supplementary Section SXX
\todo{format Jiang's paper into SI}).

@@

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX). In fact, the universal
scaling relation for $\alpha^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

\iffalse
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
theoretical findings of the linear relation between exciton binding
energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.
\fi

@@

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section S4.5) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

>>>>

for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ under small perturbation

@@

  & \alpha_{\mathrm{2D}}^{\parallel} &= \frac{2e^{2}}

@@

  & \alpha_{\mathrm{2D}}^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}

@@

rise to the different relations of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,

@@

$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the

@@

$\alpha_{\mathrm{2D}}^{\perp}$ is actually proportional to the size of potential

@@

  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\

@@

  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta

@@

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section SXX) \todo{note}, we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.

@@

corresponds well with theoretical investigations (details see
Supplementary Section SXX \todo{format Jiang's paper into SI}).

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX). In fact, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

\iffalse
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
theoretical findings of the linear relation between exciton binding
energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha_{\mathrm{2D}}^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha_{\mathrm{2D}}^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.
\fi

@@

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section S4.5) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}
